---
title: "Hello R"
author: "Jonathan Aguilar"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 5
    highlight: tango
    theme: flatly
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

This is a data frame with 1846 rows and 3 variables.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Next, we'll plot the data in the star data set.

```{r plot-star, fig.height=3, fig.width=4}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Then we calculate the correlation between `x` and `y`.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Compared to dino data the correlation for star data is slightly less.

### Exercise 4

Then we plot we plot the data in circle data set.

```{r fig.height=4, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next we calculate the corralation between `x` and `y`.

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

Compared to the dino data the correlation for circle data is higher.

### Exercise 5

Finally, we plot all datasets at once and calculate their summary correlation coefficients.

```{r fig.height=6, fig.width=7}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

```{r fig.height=5, fig.width=7}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y))
```